\papertitle

### 2014-03-16 final-report/paper.tex
Xspace

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Visualizing Physical Query Execution in a Relational Big Data Management System},
pdfauthor={Umar Javed, Thierry Moreau, Dominik Moritz, Adriana Szekeres},
pdfkeywords={},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}
\newcommand{\comment}[1]{}
\definecolor{Orange}{rgb}{1,0.5,0}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}
\newcommand{\system}{OGEN }

@@

\title{Visualizing Physical Query Execution in a Relational Big Data Management System}
\numberofauthors{1}
\author{\alignauthor Umar Javed, Thierry Moreau, Dominik Moritz, Adriana Szekeres \\
\affaddr{Dept. of Computer Science, University of Washington} \\ \affaddr{ Seattle, Washington, USA} \\
\email{\texttt{\{ujaved, moreau, domoritz, aaasz\}@cs.washington.edu}}
}

@@

Dapper and X-trace focus on how data flows through a distributed system. In \system the user looks at the operators and how the data flows through them. This orthogonal view is better suited for debugging performance bottlenecks in distributed DBMS and also scales to a larger number of events. Furthermore, in contrast to  we offer different abstraction levels, which enables users to find problems faster and handle larger amounts of profiling data. Also, \system is specifically designed to help developers understand query execution in distributed database system like Myria as opposed to general traces in distributed systems.

>>>>

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}

\hypersetup{%
pdftitle={\papertitle},
pdfauthor={Umar Javed, Thierry Moreau, Dominik Moritz, Adriana Szekeres},
pdfkeywords={},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}
\newcommand{\comment}[1]{}
\definecolor{Orange}{rgb}{1,0.5,0}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}

@@

\title{\papertitle}
\numberofauthors{1}
\author{\alignauthor Umar Javed, Thierry Moreau, Dominik Moritz, Adriana Szekeres \\
\affaddr{Dept. of Computer Science, University of Washington} \\ \affaddr{ Seattle, Washington, USA} \\
\email{\texttt{\{ujaved, moreau, domoritz, aaasz\}@cs.washington.edu}}
}

@@

Dapper and X-trace focus on how data flows through a distributed system. In \system the visualization focuses on the operators and how the data flows through them. This orthogonal view is better suited for debugging performance bottlenecks in distributed DBMS and also scales to a larger number of events. Furthermore, in contrast to  we offer different abstraction levels, which enables users to find problems faster and handle larger amounts of profiling data. Also, \system is specifically designed to help developers understand query execution in distributed database system like Myria as opposed to general traces in distributed systems.
